---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gdalgrid

<!-- badges: start -->
<!-- badges: end -->

The goal of gdalgrid is just a friendly wrapper around GDAL's [gdal_grid](https://gdal.org/programs/gdal_grid.html)

## Installation

You can install the development version of gdalgrid from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/gdalgrid")
```

## Example

This is a basic example, compare to the triangulation interpolation in the geometry package. 

```{r example}
library(gdalgrid)
library(guerrilla)
xyz <- quakes[c("long", "lat", "depth")]
x1 <- tri_fun(xyz[,1:2], xyz[,3, drop = TRUE], 
              grid = raster::raster(raster::extent(range(xyz[,1]), range(xyz[,2])), res = .1))
library(raster)
plot(x1)         
x0 <- gdal_grid(xyz, dimension = dim(x1)[2:1], extent = c(range(xyz[,1]), range(xyz[,2])))
ximage::ximage(x0, asp = 1)
```


I just wrote this as a way to time with the disussion in this issue ['Extreme performance regression in gdal_grid with method linear'](https://github.com/OSGeo/gdal/issues/1879). Looks like there's a problem with results outside the convex hull .... 



## Code of Conduct
  
Please note that the gdalgrid project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
